Maragra and Malaria: preliminary analysis

### 2017-08-30 inst/rmd/maragra_preliminary_analysis.Rmd
big update with census

---
date: ""
fig_height: 2.6
fig_width: 4
output:
  html_document:
    css: resources/style.css
    pandoc_args: [
      "+RTS", "-K16000m",
      "-RTS"
    ]
---

@@

<p style="text-align:left;">
[www.economicsofmalaria.com](www.economicsofmalaria.com)
<span style="float:right;">joebrew@gmail.com</span>
</p>

```{r}
# Read in data
ab <- maragra::ab
ab_panel <- maragra::ab_panel
clinic <- maragra::clinic
clinic_agg <- maragra::clinic_agg
mc <- maragra::mc
workers <- maragra::workers
```

# Maragra and Malaria: preliminary analysis {.tabset}

@@

```{r}
ggplot(data = y,
       aes(x = date,
           y = val,
           group = key,
           fill = key)) +
  geom_area(stat = 'identity', position = 'stack', alpha = 0.5) +
  xlab('Date') +
  ylab('Number of positive cases') +
  theme_maragra() +
  scale_fill_manual(name = '',
                    values = c('black', 'darkred')) +
  ggtitle('Malaria miscroscopy tests and positive results',
          'All workers, absolute') +
    theme(title = element_text(size = 12))
```

@@

```{r}
ggplot(data = x,
       aes(x = date,
           y = pp)) +
  geom_area(stat = 'identity', fill = 'darkblue', alpha = 0.5) +
  xlab('Date') +
  ylab('Number of positive cases') +
  theme_maragra() +
  ggtitle('Malaria miscroscopy tests and positive results',
          'All workers, relative') +
    theme(title = element_text(size = 12))

@@

```{r}
ggplot(data = x,
       aes(x = date,
           y = p,
           fill = severity)) +
  geom_area(stat = 'identity',
           position = 'stack',
           alpha = 0.6) +
  scale_fill_manual(name = 'Severity',
                    values = cols) +
  theme_maragra() +
  labs(x = 'Date',
       y = 'Percentage of all cases',
       title = 'Distribution of severity of cases over time')
```

>>>>

---
title: "Maragra and Malaria: preliminary analysis"
date: ""
fig_height: 2.6
fig_width: 4
output:
  html_document:
    toc: True
    css: resources/style.css
    pandoc_args: [
      "+RTS", "-K16000m",
      "-RTS"
    ]
---

@@

<hr>
<p style="text-align:left;">
[http://economicsofmalaria.com](http://economicsofmalaria.com)
<span style="float:right;">joebrew@gmail.com</span>
</p>
<hr>

```{r}
# Read in data
ab <- maragra::ab
ab_panel <- maragra::ab_panel
bairros <- maragra::bairros
census <- maragra::census
clinic <- maragra::clinic
clinic_agg <- maragra::clinic_agg
mc <- maragra::mc
workers <- maragra::workers
```

@@

```{r}
ggplot(data = y,
       aes(x = date,
           y = val,
           group = key,
           fill = key)) +
  geom_bar(stat = 'identity', position = 'stack', alpha = 0.5) +
  xlab('Date') +
  ylab('Number of positive cases') +
  theme_maragra() +
  scale_fill_manual(name = '',
                    values = c('black', 'darkred')) +
  ggtitle('Malaria miscroscopy tests and positive results',
          'All workers, absolute') +
    theme(title = element_text(size = 12))
```

@@

```{r}
ggplot(data = x,
       aes(x = date,
           y = pp)) +
  geom_bar(stat = 'identity', fill = 'darkblue', alpha = 0.5) +
  xlab('Date') +
  ylab('Number of positive cases') +
  theme_maragra() +
  ggtitle('Malaria miscroscopy tests and positive results',
          'All workers, relative') +
    theme(title = element_text(size = 12))

@@

```{r}
ggplot(data = x,
       aes(x = date,
           y = p,
           fill = severity)) +
  geom_bar(stat = 'identity',
           position = 'stack',
           alpha = 0.6) +
  scale_fill_manual(name = 'Severity',
                    values = cols) +
  theme_maragra() +
  labs(x = 'Date',
       y = 'Percentage of all cases',
       title = 'Distribution of severity of cases over time')
```
